Analysis

### 2019-12-02 analysis.Rmd
grafico cambio error

bar3 <- ggplot(table_gap_total, aes(as.factor(year),median)) +
      geom_bar(aes(fill = factor(ocup, levels=c(1,2), labels=c("percepcion", "justicia"))), position = "dodge", stat="identity", width=.5)  +
      geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), group="Ocup"), position=position_dodge(width=0.5), vjust=-0.5) +
      theme_bw(base_size = 18) +
      scale_y_continuous(labels = scales::comma) +
      ylab('Brecha (mediana)') + xlab('Años') +
      scale_fill_brewer(palette="Paired") +
      theme(legend.position="top") +
      labs(fill = " ") # quitar nombre leyenda, autoexplicativo +

>>>>

bar3 <- ggplot(table_gap_total, aes(as.factor(year),median)) +
      geom_bar(aes(fill = factor(ocup, levels=c(1,2), labels=c("justa ", "percibida"))), position = "dodge", stat="identity", width=.5)  +
      geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), group="Ocup"), position=position_dodge(width=0.5), vjust=-0.5) +
      theme_bw(base_size = 18) +
      scale_y_continuous(labels = scales::comma) +
      ylab('Brecha (mediana)') + xlab('Años') +
      scale_fill_brewer(palette="Paired") +
      theme(legend.position="top") +
      labs(fill = " ") # quitar nombre leyenda, autoexplicativo +
